Current state and prospects of R-packages for the design of experiments

### 2022-06-11 paper.Rmd
discussion added

---
title: Current state and prospects of R-packages for the design of experiments
author:
  - name: Emi Tanaka
    affiliation: Monash University
  - name: Dewi Amaliah 
    affiliation: Monash University
abstract: >
    Re-running an experiment is generally costly and in some cases impossible due to limited resources, so the design of an experiment plays a critical role in increasing the quality of experimental data.  In this article we describe the current state of the R-packages for the design of experiments through an exploratory data analysis of package downloads, package metadata, and the comparison of characteristics with other topics. We observe that experimental designs in practice appear to be sufficiently manufactured by a small number of packages and the development of experimental designs occur in silos. We discuss also the interface designs of widely utilised R packages in the field of experimental design and discuss its future prospects for the field.
bibliography: paper.bib
knit: (function(inputFile, encoding) { rmarkdown::render(inputFile, encoding = encoding, output_file = file.path(dirname(inputFile), 'index.html')) })
keywords: ["experimental design", "CRAN task view", "user interface", "application programming interface", "software design"]
output: 
  bookdown::html_document2: 
    theme: paper
  # below is to have a JSS paper style template
  pagedown::jss_paged:
    template: assets/html-template.html
    csl: assets/html-template.csl
    self_contained: false
---

@@

Volunteer maintained -- some experimental design packages may not be included in the CRAN task view.

>>>>

---
title: Current state and prospects of R-packages for the design of experiments
author:
  - name: Emi Tanaka
    affiliation: Monash University
  - name: Dewi Amaliah 
    affiliation: Monash University
abstract: >
    Re-running an experiment is generally costly and in some cases impossible due to limited resources, so the design of an experiment plays a critical role in increasing the quality of experimental data.  In this article we describe the current state of the R-packages for the design of experiments through an exploratory data analysis of package downloads, package metadata, and the comparison of characteristics with other topics. We observe that experimental designs in practice appear to be sufficiently manufactured by a small number of packages and the development of experimental designs occur in silos. We discuss also the interface designs of widely utilised R packages in the field of experimental design and discuss its future prospects for the field.
bibliography: paper.bib
knit: (function(inputFile, encoding) { rmarkdown::render(inputFile, encoding = encoding, output_file = file.path(dirname(inputFile), 'index.html')) })
keywords: ["experimental design", "CRAN task view", "user interface", "application programming interface", "software design"]
output: 
  #bookdown::html_document2: 
  #  theme: paper
  # below is to have a JSS paper style template
  pagedown::jss_paged:
    template: assets/html-template.html
    csl: assets/html-template.csl
    self_contained: false
---

@@

Through the exploratory data analysis of three data sources (package download logs, package metadata and CRAN task views) outlined in Section \@ref(data), we have observed that the the total download of DoE packages are concentrated only on a handful of R-packages although these represent a diverse set in comparison with other CRAN task views. Furthermore, the data suggests that the field of experimental design is the least collaborative field; out of all CRAN task views, it has one of the least average number of authors and the lowest intra-connectivity (any dependency on other packages within its own task view). 
There are a number of limitations and short coming in our exploratory data analysis. First, CRAN task views are volunteer maintained so some experimental design packages may not be included in the DoE packages. Second, we only use the RStudio CRAN mirror download, which may bias our observations. Third, our analysis are limited to R-packages alone, although the sheer quantity and variation of experimental design is unmatched with any other programming languages. Finally, all our statements should be treated as speculative rather than conclusive; the data are all observational so no conclusive, generalisable statement are possible. Regardless, the data driven nature of our analysis give an objective insight into the field of experimental design.

The interface design (discussed in Section \@ref(design)) reveals that the most widely used DoE packages generally have functions that is 1) a menu format (i.e. the name of the function correspond to a particular recipe of the design or optimal search algorithm) and 2) context is often a second-thought (e.g. only the number of factors is needed and the package will assign pseudo factor names or an argument exists for optional input of character vector that corresponds to the factor names).

### 2022-06-11 paper/arxiv/arxiv.tex
discussion added

\title{Current status and prospects of R-packages for the design of
experiments}

@@

\begin{abstract}
Re-running an experiment is generally costly and in some cases
impossible due to limited resources, so the design of an experiment
plays a critical role in increasing the quality of experimental data. In
this article we describe the current state of the R-packages for the
design of experiments through exploratory data analysis of package
downloads, package metadata, and comparison of characteristics with
other topics. We discuss also the software design of widely utilised R
packages in the field of experimental design and conclude with
discussion of some future prospects for the field.
\end{abstract}

@@

The critical role of data collection is well captured in the expression
``garbage in, garbage out'' -- in other words, if the collected data is
rubbish then no analysis, however complex it may be, can make something
out of it. Methods for data collection can be dichotomised by the type
of data collected -- namely, experimental or observational -- or
alternatively, categorised as experimental design (including
quasi-experimental design) or survey design. This dichotomisation, to a
great extent, is seen in the
\href{https://cran.r-project.org/web/views/}{CRAN task views} (a
volunteered maintained list of R-packages by topic) where R-packages in
experimental design are in ctv\{ExperimentalDesign\} and R-packages in
survey designs are in ctv\{OfficialStatistics\}. Experimental designs
exclusively center on the collection of experimental data where many of
the experimental factors tend to be in the control of the experimenter.
A subset of experimental designs are segregated into
ctv\{ClinicalTrials\}, where the focus is on clinical trials with
primary interest in sample size calculations. This paper focuses on the
packages in ctv\{ExperimentalDesign\}, henceforth referred to as ``DoE
packages''.

In the CRAN task view of ctv\{ExperimentalDesign\}, there are 114 R
packages for experimental design and analysis of data from experiments.
The sheer quantity and variation of experimental designs in the
R-packages are arguably unmatched with any other programming languages,
e.g.~in Python (Rossum 1995), only a handful of libraries that generate
design of experiment exist (namely \texttt{pyDOE}, \texttt{pyDOE2},
\texttt{dexpy}, \texttt{experimenter} and \texttt{GPdoemd}) with limited
type of designs. Thus, the study of DoE packages can be revealing into
the current status of the field of experimental design.

@@

\caption{The points show the Gini index of the download counts by year facetted by CRAN task view with the color showing the number of packages. The grey line shows the distribution of the Gini index across years for all other CRAN task views. The facets are ordered by increasing value of the Gini index in 2021.}\label{fig:fig-gini-all-ctvs}
\end{figure}

@@

\begin{itemize}
\tightlist
\item
  The increase in the number of packages that are not highly downloaded
  may mean that \textbf{\emph{there are more packages to construct niche
  experimental designs}}. Some examples of these packages include
  \texttt{qtlDesign}, \texttt{PwrGSD} and \texttt{Crossover} made for
  QTL experiments, group sequential designs and crossover trials,
  respectively. These packages would naturally have a smaller number of
  potential users. Counterfactual to this, the increase could be due to
  other external factors, such as an increase in a number of skilled
  contributors, a change in CRAN policy or management to add packages
  (either to CRAN and/or task view), and/or that new packages are still
  yet to amass users. While there is an argument that low download
  counts are due to the low utility and/or quality of the packages,
  packages in CRAN task views are selected by expert maintainers; thus
  we can reasonably assume that any package listed in CRAN task view are
  of a decent utility and quality.
\item
  If the downloads are reflective of the experimental designs used in
  practice, \textbf{\emph{small set of packages appear to be sufficient
  for most to construct the full set of designs of experiments needed in
  practice}}. Packages of course evolve and the top downloaded packages
  have had regular updates that may have broadened its scope.
\item
  While small subset of DoE packages are most frequently used, none of
  these packages are dominant in the field (judging from comparisons
  with other CRAN task views). This suggests that there are
  \textbf{\emph{diverse approaches to designing experiments}}. This
  observation doesn't take into account other approaches to generating
  experimental designs, like the proprietary GUI software, CycDesignN,
  which may be widely used.
\end{itemize}

@@

In software design, there are two interface designs to consider: user
interface (UI) and application programming interface (API). UI is
concerned with the usage of the software by the user, while the API is
concerned with how different programs interact and is predominately of
the interest to the developer. In this section, we discuss these
interface designs broadly, with examples illustrated from the top
downloaded packages (as shown in Figure @ref(fig:rank-over-time)). We
exclude \texttt{ez} and \texttt{DiceKriging} from the discussion as the
former is predominately visualisation of experimental data and latter is
about the analysis of computer experiments in addition to belonging to
the same suite of packages as \texttt{DiceDesign}.

\hypertarget{the-case-of-specialised-designs}{%
\subsection{The case of specialised
designs}\label{the-case-of-specialised-designs}}

In this section, we present some examples the user interface of widely
used specialised designs, namely, computer experiments, factorial
experiments, response surface designs and sequential designs.

Computer experiments, as discussed in Section @ref(topics), which
generally involve space filling designs have been on the rise. The
exemplar for this type of designs are \texttt{lhs} and
\texttt{DiceDesign}. For the \texttt{lhs} package, functions like
\texttt{randomLHS()}, \texttt{optimumLHS()}, and \texttt{maximinLHS()}

Factorial experiments offer a challenge in the construction and
allocation of the treatment factors. This is reflected in a number of
packages that specifically addresses this challenge. These include
\texttt{DoE.base} (Grömping 2018), \texttt{FrF2} (Grömping 2014) for
fractional 2-level factorial designs, \texttt{conf.design} (Venables
2013), \texttt{FrF2.catlg128} (Grömping 2022) and \texttt{BHH2} (Barrios
2016).

Response surface design, as illustrated by \texttt{rsm} (Lenth 2009), is
a type of experiment that involve variables with continuous measures.

Finally, another specialised design is sequential design (also called
adaptive sampling), which is best represented by \texttt{tgp} (Gramacy
and Taddy 2010) -- these require prior information, which are used to
inform the next experimental design. Follow-up experiments, which can
also be classified as a sequential design, is implemented by
\texttt{BsMD} (Barrios 2020).

@@

The \texttt{agricolae} package (de Mendiburu 2021) was the most
downloaded DoE packages in 2013 to 2018 (Figure
@ref(fig:rank-over-time)) and possibly prior to 2013 (data unavailable).
This package is the prime example of constructing designs based on menu
functions, e.g.~\texttt{design.crd()}, \texttt{design.rcbd()} and
\texttt{design.split()} construct a completely randomised design,
randomised complete block design and split-plot design, respectively.
Users typically supply the treatment labels and the number of
replications as argument to these functions.

\hypertarget{the-case-of-general-designs}{%
\subsection{The case of general
designs}\label{the-case-of-general-designs}}

\texttt{AlgDesign} (Wheeler 2022)

@@

Volunteer maintained -- some experimental design packages may not be
included in the CRAN task view.

@@

This paper uses the \texttt{targets} framework (Landau 2021) for
reproducibility, \texttt{knitr} (Xie 2015) and \texttt{rmarkdown} (Xie,
Allaire, and Grolemund 2018) for creating reproducible documents,
\texttt{ggplot2} (Wickham 2016) for visualisation and
\texttt{kableExtra} (Zhu 2021) for customising the table. All code to
reproduce this paper is found at
\url{https://github.com/emitanaka/paper-DoE-review}.

@@

@@

@@

@@

@@

@@

@@

@@

@@

>>>>

\title{Current state and prospects of R-packages for the design of
experiments}

@@

\begin{abstract}
Re-running an experiment is generally costly and in some cases
impossible due to limited resources, so the design of an experiment
plays a critical role in increasing the quality of experimental data. In
this article we describe the current state of the R-packages for the
design of experiments through an exploratory data analysis of package
downloads, package metadata, and the comparison of characteristics with
other topics. We observe that experimental designs in practice appear to
be sufficiently manufactured by a small number of packages and the
development of experimental designs occur in silos. We discuss also the
interface designs of widely utilised R packages in the field of
experimental design and discuss its future prospects for the field.
\end{abstract}

@@

The critical role of data collection is well captured in the expression
``garbage in, garbage out'' -- in other words, if the collected data is
rubbish then no analysis, however complex it may be, can make something
out of it. A carefully crafted data collection scheme is therefore
critical to optimise the information from data. Of all the data
collection schemes, the field of experimental designs is specifically
devoted to planning an experiment largely based on the founding
principles by Fisher (1935) or an optimisation framework like those
described in Pukelsheim (2006). These experimental designs are often
constructed with the aid of a statistical software, such as R (R Core
Team 2021), so software usage can aid in understanding the practice of
experimental design. Given the large gain that can be made from
collecting higher quality experimental data, we benefit from
understanding the current state of the experimental designs in practice.

Methods for data collection can be dichotomised by the type of data
collected -- namely, experimental or observational -- or alternatively,
categorised as experimental design (including quasi-experimental design)
or survey design. This dichotomisation, to a great extent, is seen in
the \href{https://cran.r-project.org/web/views/}{Comprehensive R Archive
Network (CRAN) task views} (a volunteer maintained list of R-packages by
topic) where R-packages in experimental design are in
ctv\{ExperimentalDesign\} task view and R-packages in survey designs are
in ctv\{OfficialStatistics\} task view. The full list of available
topics can be see in Table S1 in the Supplementary Materials and also
accessed via the \texttt{ctv} package (Zeileis 2005). A subset of
experimental designs are segregated into ctv\{ClinicalTrials\} task
view, where the focus is on clinical trials with primary interest in
sample size calculations. This paper focuses on the packages in
ctv\{ExperimentalDesign\} task view, henceforth referred to as ``DoE
packages''.

In ctv\{ExperimentalDesign\} task view, there are 114 R packages for
experimental design and analysis of data from experiments. The sheer
quantity and variation of experimental designs in the R-packages are
arguably unmatched with any other programming languages, e.g.~in Python
(Rossum 1995), only a handful of libraries that generate design of
experiment exist (namely \texttt{pyDOE}, \texttt{pyDOE2},
\texttt{dexpy}, \texttt{experimenter} and \texttt{GPdoemd}) with limited
type of designs. Thus, the study of DoE packages, based on quantitative
and qualitative data, can give us an objective view to the state of the
current experimental designs in practice.

A utility of software can also be described by its design to facilitate
clear expression and interpretation of the desired experimental design.
Certain programming language design can hinder or discourage development
of a reliable program (Wasserman 1975). The immense popularity of
\texttt{tidyverse} (a collection of R-packages for various stages of
data analysis that place enormous emphasis on the interface design by
Wickham et al. 2019) is a testament to the impact an interface design
can have in practice.

@@

\caption{The points show the Gini index of the download counts by year for ExperimentalDesign CRAN task view with the color showing the number of packages. The grey line shows the distribution of the Gini index across years for all other CRAN task views. See Figure S2 in the Supplementary Material for the line graph for the Gini index across years by each CRAN task view.}\label{fig:fig-gini-all-ctvs}
\end{figure}

@@

\begin{itemize}
\tightlist
\item
  The increase in the number of packages that are not highly downloaded
  may mean that \textbf{\emph{there are more packages to construct niche
  experimental designs}}. Some examples of these packages include
  \texttt{qtlDesign}, \texttt{PwrGSD} and \texttt{Crossover} made for
  QTL experiments, group sequential designs and crossover trials,
  respectively. These packages would naturally have a smaller number of
  potential users. Counterfactual to this, the increase could be due to
  other external factors, such as an increase in a number of skilled
  contributors, a change in CRAN policy or management to add packages
  (either to CRAN and/or task view), and/or that new packages are still
  yet to amass users. While there is an argument that low download
  counts are due to the low utility and/or quality of the packages,
  packages in CRAN task views are selected by expert maintainers; thus
  we can reasonably assume that any package listed in CRAN task view are
  of a decent utility and quality.
\item
  If the downloads are reflective of the experimental designs used in
  practice, \textbf{\emph{small set of packages appear to be sufficient
  for most to construct the full set of designs of experiments needed in
  practice}}. Packages of course evolve and the top downloaded packages
  have had regular updates that may have broadened its scope.
\item
  While small subset of DoE packages are most frequently used, none of
  these packages are dominant in the field (judging from comparisons
  with other CRAN task views). This suggests that there are
  \textbf{\emph{diverse approaches to designing experiments}}. This
  observation doesn't take into account other approaches to generating
  experimental designs, like the proprietary software, CycDesignN
  (Whittaker, Williams, and John 2022) and SAS (SAS Institute 1985),
  which may be widely used.
\end{itemize}

@@

In software design, there are two interface designs to consider: user
interface (UI) and application programming interface (API). UI is
concerned with the interaction of the software by the user, while the
API is concerned with how different programs interact and is
predominately of the interest to the developer. The UI design is an
abstraction to specifying the desired experimental design and its
choices enable how a user expresses the specification of the
experimental design.

In this section, we discuss these interface designs broadly, with
examples illustrated from the top downloaded packages (shown in Figure
@ref(fig:rank-over-time)). We exclude \texttt{ez} and
\texttt{DiceKriging} from the discussion as the former is predominately
visualisation of experimental data and latter is about the analysis of
computer experiments in addition to belonging to the same suite of
packages as \texttt{DiceDesign}.

\hypertarget{the-case-of-space-filling-and-optimal-designs}{%
\subsection{The case of space-filling and optimal
designs}\label{the-case-of-space-filling-and-optimal-designs}}

Computer experiments, as discussed in Section @ref(topics), which
generally involve space filling designs, have been on the rise. The
exemplar for this type of designs are \texttt{lhs} and
\texttt{DiceDesign}. For the \texttt{lhs} package, functions like
\texttt{randomLHS()}, \texttt{optimumLHS()}, and \texttt{maximinLHS()},
require users to specify the sample size (\(n\)) and the number of
variables (\(p\)) then it generates a Latin hypercube sample, based on
different optimisation schemes (in this case, random, S optimal and
maxmin criteria, respectively; see package documentation for more
details). Similarly for the \texttt{DiceDesign}, there is a
comprehensive list of space-filling designs such as
\texttt{dmaxDesign()}, \texttt{lhsDesign()}, \texttt{straussDesign()}
and \texttt{wspDesign()} with input of \(n\) and \(p\) as before (among
extra parameters for some) that implement algorithms that either
maximise the entropy, produce a random Latin hypercube sample, based on
Strauss process and WSP algorithm, respectively. These designs all
output a \(n \times p\) matrix with values between 0 and 1.

The \texttt{AlgDesign} (Wheeler 2022) package offers three primary
functions for generating optimal designs: \texttt{optBlock()},
\texttt{optFederov()} and \texttt{optMonteCarlo()}. These functions in
general require a formula in terms of the supplied terms with the choice
of criterion (D, A and I for the latter two). The difference lies in the
search algorithm for the optimal design.

\hypertarget{the-case-of-factorial-designs}{%
\subsection{The case of factorial
designs}\label{the-case-of-factorial-designs}}

Factorial experiments offer a challenge in the construction and
allocation of the treatment factors. This is reflected in a number of
packages that specifically addresses this challenge. These include
\texttt{DoE.base} (Grömping 2018) for full factorial and (regular and
irregular) orthogonal array designs via \texttt{fac.design()} and
\texttt{oa.design()}, respectively, \texttt{FrF2} (Grömping 2014) for
fractional 2-level factorial designs using \texttt{FrF2()},
\texttt{FrF2Large()} or \texttt{pb()} Plankett-Burnman designs (Plackett
and Burman 1946), \texttt{conf.design} (Venables 2013) for symmetric
confounded factorial designs via \texttt{conf.design()}, and
\texttt{BHH2} (Barrios 2016) to generate full or fractional 2-level
factorial design matrix via \texttt{ffDesMatrix()}. All these designs
generally requires the user to input the number of factors and if the
design is allowed to vary in the number of levels, the input of the
number of levels for each factor. The construction of some of these
designs are catalogue-based, e.g.~\texttt{oa.design()} in
\texttt{DoE.base} and the entire package \texttt{FrF2.catlg128}
(Grömping 2022) is a list of fractional 2-level factorial designs.

Response surface design, as illustrated by \texttt{rsm} (Lenth 2009), is
a factorial experiment but the focus of it is to analyse using response
surface modelling. The two well known response surface designs are
Box-Behnken design (Box and Behnken 1960) and central-composite designs
(Box and Wilson 1951) via \texttt{bbd()} and \texttt{ccd()} for
central-composite designs providing formula.

\hypertarget{the-case-of-sequential-designs}{%
\subsection{The case of sequential
designs}\label{the-case-of-sequential-designs}}

Another specialised design is sequential design (also called adaptive
sampling), which is best represented by \texttt{tgp} (Gramacy and Taddy
2010) -- these require prior information, which are used to inform the
next experimental design using \texttt{tgp.design()} and
\texttt{dopt.gp()} which requires users to supply candidate samples to
sub-sample from and a model or design from a prior design. Follow-up
experiments, which can also be classified as a sequential design, is
implemented by \texttt{BsMD} (Barrios 2020). In \texttt{BsMD}, the
follow-up design is determined by a model discriminant approach using
\texttt{MD()}.

@@

The \texttt{agricolae} package (de Mendiburu 2021) was the most
downloaded DoE packages in 2013 to 2018 (Figure
@ref(fig:rank-over-time)) and possibly prior to 2013 (data unavailable).
This package is the prime example of constructing designs based on menu
functions, e.g.~\texttt{design.crd()}, \texttt{design.rcbd()} and
\texttt{design.split()} construct a completely randomised design,
randomised complete block design and split-plot design, respectively.
Users typically supply the treatment labels (or number of treatments in
the case of \texttt{design.split()}) and the number of replications as
argument to these functions.

@@

Through the exploratory data analysis of three data sources (package
download logs, package metadata and CRAN task views) outlined in Section
@ref(data), we have observed that the the total download of DoE packages
are concentrated only on a handful of R-packages although these
represent a diverse set in comparison with other CRAN task views.
Furthermore, the data suggests that the field of experimental design is
the least collaborative field; out of all CRAN task views, it has one of
the least average number of authors and the lowest intra-connectivity
(any dependency on other packages within its own task view). There are a
number of limitations and short coming in our exploratory data analysis.
First, CRAN task views are volunteer maintained so some experimental
design packages may not be included in the DoE packages. Second, we only
use the RStudio CRAN mirror download, which may bias our observations.
Third, our analysis are limited to R-packages alone, although the sheer
quantity and variation of experimental design is unmatched with any
other programming languages. Finally, all our statements should be
treated as speculative rather than conclusive; the data are all
observational so no conclusive, generalisable statement are possible.
Regardless, the data driven nature of our analysis give an objective
insight into the field of experimental design.

The interface design (discussed in Section @ref(design)) reveals that
the most widely used DoE packages generally have functions that is 1) a
menu format (i.e.~the name of the function correspond to a particular
recipe of the design or optimal search algorithm) and 2) context is
often a second-thought (e.g.~only the number of factors is needed and
the package will assign pseudo factor names or an argument exists for
optional input of character vector that corresponds to the factor
names).

@@

This paper uses the \texttt{targets} framework (Landau 2021) for
reproducibility, \texttt{knitr} (Xie 2015) and \texttt{rmarkdown} (Xie,
Allaire, and Grolemund 2018) for creating reproducible documents,
\texttt{ggplot2} (Wickham 2016), \texttt{ggraph} (Pedersen 2021),
\texttt{ggwordcloud} (Le Pennec and Slowikowski 2019) and
\texttt{colorspace} (Zeileis et al. 2020) for visualisation,
\texttt{kableExtra} (Zhu 2021) for customising the table in the
Supplementary Material and \texttt{tidyverse} (Wickham et al. 2019),
\texttt{tidytext} (Silge and Robinson 2016), \texttt{pluralize} (Rudis
and Embrey 2020), and \texttt{ineq} (Zeileis 2014) for data processing
and manipulation, and \texttt{cranlogs} (Csárdi 2019) and \texttt{ctv}
(Zeileis 2005) for extracting data. All code to reproduce this paper is
found at \url{https://github.com/emitanaka/paper-DoE-review}.

@@

\leavevmode\vadjust pre{\hypertarget{ref-Box1960-wr}{}}%
Box, G E P, and D W Behnken. 1960. {``Some New Three Level Designs for
the Study of Quantitative Variables.''} \emph{Technometrics: A Journal
of Statistics for the Physical, Chemical, and Engineering Sciences} 2
(4): 455--75. \url{https://doi.org/10.2307/1266454}.

\leavevmode\vadjust pre{\hypertarget{ref-Box1951-ji}{}}%
Box, G E P, and K B Wilson. 1951. {``On the Experimental Attainment of
Optimum Conditions.''} \emph{Journal of the Royal Statistical Society.
Series B, Statistical Methodology} 13 (1): 1--45.

@@

\leavevmode\vadjust pre{\hypertarget{ref-Fisher1935-qc}{}}%
Fisher, Ronald. 1935. \emph{The Design of Experiments}. Oliver; Boyd.

@@

\leavevmode\vadjust pre{\hypertarget{ref-ggwordcloud}{}}%
Le Pennec, Erwan, and Kamil Slowikowski. 2019. \emph{Ggwordcloud: A Word
Cloud Geom for 'Ggplot2'}.
\url{https://CRAN.R-project.org/package=ggwordcloud}.

@@

\leavevmode\vadjust pre{\hypertarget{ref-ggraph}{}}%
Pedersen, Thomas Lin. 2021. \emph{Ggraph: An Implementation of Grammar
of Graphics for Graphs and Networks}.
\url{https://CRAN.R-project.org/package=ggraph}.

\leavevmode\vadjust pre{\hypertarget{ref-Plackett1946-ly}{}}%
Plackett, R L, and J P Burman. 1946. {``The Design of Optimum
Multifactorial Experiments.''} \emph{Biometrika} 33 (4): 302--25.

\leavevmode\vadjust pre{\hypertarget{ref-Pukelsheim2006-sv}{}}%
Pukelsheim, Friedrich. 2006. \emph{Optimal Design of Experiments}.

\leavevmode\vadjust pre{\hypertarget{ref-R}{}}%
R Core Team. 2021. \emph{R: A Language and Environment for Statistical
Computing}. Vienna, Austria: R Foundation for Statistical Computing.
\url{https://www.R-project.org/}.

@@

\leavevmode\vadjust pre{\hypertarget{ref-pluralize}{}}%
Rudis, Bob, and Blake Embrey. 2020. \emph{Pluralize: Pluralize and
'Singularize' Any (English) Word}.
\url{https://CRAN.R-project.org/package=pluralize}.

\leavevmode\vadjust pre{\hypertarget{ref-sas1985sas}{}}%
SAS Institute. 1985. \emph{SAS User's Guide: Statistics}. Vol. 2. Sas
Inst.

\leavevmode\vadjust pre{\hypertarget{ref-tidytext}{}}%
Silge, Julia, and David Robinson. 2016. {``Tidytext: Text Mining and
Analysis Using Tidy Data Principles in r.''} \emph{JOSS} 1 (3).
\url{https://doi.org/10.21105/joss.00037}.

@@

\leavevmode\vadjust pre{\hypertarget{ref-Wasserman1975-xr}{}}%
Wasserman, Anthony I. 1975. {``Issues in Programming Language Design -
an Overview.''} In.

@@

\leavevmode\vadjust pre{\hypertarget{ref-cycdesignn}{}}%
Whittaker, D., E. R. Williams, and J. A John. 2022. \emph{CycDesign: A
Package for the Computer Generation of Experimental Designs,} (version
7.0). \url{https://vsni.co.uk/software/cycdesign}.

@@

\leavevmode\vadjust pre{\hypertarget{ref-Wickham2019-mj}{}}%
Wickham, Hadley, Mara Averick, Jennifer Bryan, Winston Chang, Lucy
D'agostino McGowan, Romain Francois, Garrett Grolemund, et al. 2019.
{``Welcome to the Tidyverse.''} \emph{Journal of Open Source Software} 4
(43): 1686.

@@

\leavevmode\vadjust pre{\hypertarget{ref-ctv}{}}%
Zeileis, Achim. 2005. {``{CRAN} Task Views.''} \emph{R News} 5 (1):
39--40. \url{https://CRAN.R-project.org/doc/Rnews/}.

\leavevmode\vadjust pre{\hypertarget{ref-ineq}{}}%
---------. 2014. \emph{Ineq: Measuring Inequality, Concentration, and
Poverty}. \url{https://CRAN.R-project.org/package=ineq}.

\leavevmode\vadjust pre{\hypertarget{ref-colorspace}{}}%
Zeileis, Achim, Jason C. Fisher, Kurt Hornik, Ross Ihaka, Claire D.
McWhite, Paul Murrell, Reto Stauffer, and Claus O. Wilke. 2020.
{``{colorspace}: A Toolbox for Manipulating and Assessing Colors and
Palettes.''} \emph{Journal of Statistical Software} 96 (1): 1--49.
\url{https://doi.org/10.18637/jss.v096.i01}.
